Online Social Cohesion Reflects Real-World Group Action in Syria during the Arab Spring

### 2020-05-28 manuscript.Rmd
Add equations

(insert social cohesion equations here)

>>>>

\begin{align}
\text{Inverse frequency weighting of overlap words = }\sum_{i=1}^k \frac{log(f(t_i, d1) + f(t_i, d2) + 1)}{log(f(t_i) + 1)}
\end{align}

\begin{align}
\text{Inverse frequency weighting of all words = }\sum_{i=1}^n \frac{log(f(t_i, d1) + f(t_i, d2) + 1)}{log(f(t_i) + 1)}
\end{align}

\begin{align}
\text{Two tweets similarity =}\frac{\text{inverse frequency weighting of overlap words}}{\text{inverse frequency weighting of all words}}
\end{align}
